%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{cv}

% For mathematical symbols
\usepackage{amsmath}
\usepackage{fancyhdr,graphicx,xcolor,colortbl}
\usepackage{fontspec}
\usepackage[colorlinks,urlcolor=blue]{hyperref}
% Set applicant's personal data for header
\name{Ahmed Hendawy}
\address{Cairo, Egypt \linebreak +201553025327 \linebreak lildevhind@gmail.com}
\contacts{a}

\links{
	{\color{blue}\underline{\href{https://www.github.com/devhindo}{GitHub}}} \linebreak 
	{\color{blue}\underline{\href{https://www.linkedin.com/in/hindawy/}{Linkedin}}} \linebreak 
	{\color{blue}\underline{\href{https://www.leetcode.com/devhindo}{Leetcode}}}}


\begin{document}


	% Print the header
	\makeheader 



	% Print the content
		

	\begin{cvsection}{Employment}
				\vspace{3mm}

		% ITI

				\begin{cvsubsection}{Software Backend Engineer, Intern}{Information Technology Institute (ITI)}{July 2023 - August 2023 \linebreak Mansoura, Egypt}
			\vspace{2mm}

			\begin{itemize}
				\item Developed a full-stack library management system, demonstrating proficiency in end-to-end project delivery.
				\item Implemented a user-friendly admin dashboard, enhancing system accessibility and control.
				\item Created responsive UI components using Bootstrap to seamlessly interact with the Django server.
				\item \textbf{Skills:} Python; Django; PostgreSQL; Bootstrap; HTML; CSS; JavaScript.
			\end{itemize}
		\end{cvsubsection}		
		% NTI
		\begin{cvsubsection}{AI Engineer, Intern}{National Telecommunication Institute (NTI)}{July 2022 - August 2023 \linebreak Cairo, Egypt}
			\vspace{3mm}

			\begin{itemize}
				\item Implemented sophisticated image recognition algorithms, significantly enhancing the accuracy and efficiency of detection systems..
				\item Applied knowledge of Linear Algebra to optimize and fine-tune machine learning models.
				\item \textbf{Skills:} Python; TensorFlow; Jupyter Notebook; Linear Algebra 
			\end{itemize}
		\end{cvsubsection}
		

		
	
		
	\end{cvsection}
	
	\begin{cvsection}{Education}
	
	\vspace{2mm}

		\begin{cvsubsection}{Mansoura, Egypt}{Mansoura University}{Fall 2019 -- July 2024}
			\begin{itemize}
				\item Faculty of Engineering, Department of Computer Engineering and Control Systems.
				\item Pursuing B.S.E. in Computer Engineering.
				
				\item Undergraduate Coursework: Operating Systems; Databases; Data Structures; Algorithms; Programming Languages; Comp. Architecture; Computer Graphics; Linear Algebra; Calculus III; Numerical Analysis; Digital Control; PLC Design.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Technical Experience}
	\vspace{2mm}

		\begin{cvsubsection}{Projects}{}{}
			\begin{itemize}
				\item \textbf{{\color{blue}\underline{\href{https://github.com/devhindo/x}{X}}}}. CLI tool to interface with Twitter API, e.g. posting tweets.  Go, OAuth 2.0, HTTPS
				
				\item \textbf{{\color{blue}\underline{\href{https://github.com/devhindo/dearself}{dearself}}}}. mailing service to sending future mails to yourself as a message from the past, e.g. posting tweets.  Next.js, TypeScript, TailwindCSS, Go, Gin, Mailjet API

				\item \textbf{{\color{blue}\underline{\href{https://github.com/devhindo/katty}{katty}}}}. Discord bot to fetch songs' lyrics.  Go, Discord API, Musixmatch API				
				
				\item \textbf{{\color{blue}\underline{\href{https://github.com/devhindo/obliviax}{Obliviax}}}}. Chess engine implements the Universal Chess Interface protocol.  C++, OOP
				
				
				
				\item \textbf{{\color{blue}\underline{\href{https://github.com/lilhind/iti23/tree/main/library}{Library}}}}. library management system including student authentication and admin dashboard implementation.  Python, Django, PostgreSQL, HTML, CSS, JS

				\item \textbf{{\color{blue}\underline{\href{https://github.com/devhindo/doodle}{Doodle}}}}. Chrome extension where users can take notes on webpages. TypeScript, Chrome API				
				

			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Volunteering}
				\vspace{2mm}

		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item \textbf{ICPC Mansoura University (April 2022- July 2023):} Coordinated local competitive programming contests within my university, fostering a competitive and intellectually stimulating environment.
				\item \textbf{IEEE Mansoura Student Branch(August 2020- Novermber 2022):} Engaged actively in the coordination of various events, including Tech-Elixir 2.0, Career Insider 6.0, and IEEE Victoris 1.0. 
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}


	\begin{cvsection}{Languages and Technologies}
					\vspace{2mm}

		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item Object-oriented design, Test-driven development (TTD), Algorithm Design, Data Structures, Problem Solving, Complexity Analysis, Distributed Systems, Relational database, NoSQL databases
				\item JavaScript; Python; GoLang; C/C++; SQL; TypeScript; 
				\item Git; Docker; MySQL; PostgreSQL; MongoDB;Linux; Bash; LaTeX
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
\end{document}

